Case Study: Gene Set Enrichment Analysis (Human Data Set)

### 2018-04-01 datasets/GSEA/gsea-human.Rmd
Add covLinePlots to GSEA case studies

The objective of this document is to test different multiple testing methods in the context of Gene Set Enrichment Analysis (GSEA). In order to get a list of genes, we will use RNA-seq data consisting on cortex and cerebellum samples of a subset of the GTEx data.

@@

Gene set size of overlaps.

```{r}
methods <- c("lfdr", "ihw-a10", "bl-df03", "qvalue", "bh", "bonf")
plotCovariateBoxplots(sGSEA, alpha=0.1, nsets=6, methods=methods, trans=log2)
plotCovariateBoxplots(sGSEA, alpha=0.1, nsets=7, methods=methods, trans=log2, maxNum=5)
```

```{r}
estimatePerformanceMetrics( pr, alpha=0.1, tidy=TRUE ) %>%
    dplyr::filter( blabel %in% c("lfdr","ihw-a10","bl-df03","qvalue","bh", "bonf") ) %>%
    dplyr::select( blabel, value )
```

>>>>

The objective of this document is to compare different methods for multiple testing correction in the context of Gene Set Enrichment Analysis (GSEA). In order to get a list of genes, we will use RNA-seq data consisting of cortex and cerebellum samples of a subset of the GTEx data.

@@

```{r}
covariateLinePlot(sGSEA, alpha = 0.1, covname = "ind_covariate")
```
